---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# tennistools

<!-- badges: start -->
<!-- badges: end -->

The goal of tennistools is to make working with tennis data a little easier.
It provides helper functions for score calling, set validation, training group
division, and round-robin schedule generation — useful for coaches, players,
and anyone organising a tennis tournament.

## Installation

You can install the development version of tennistools from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("benvandonselaar/tennistools")
```

## Usage

### `call_score()`

A common need during a match is translating raw point counts into the official
tennis score call. `call_score()` handles all standard situations: opening,
normal points, deuce, advantage, and game.

```{r}
library(tennistools)

call_score(0, 0)   # start of a game
call_score(1, 2)   # fifteen, thirty
call_score(3, 3)   # deuce
call_score(4, 3)   # advantage server
call_score(4, 1)   # game server
```

### `is_set_won()`

To check whether a set is finished, use `is_set_won()`. It follows standard
ATP/WTA rules, including the 7-5 and tiebreak (7-6) edge cases.

```{r}
is_set_won(6, 4)   # TRUE
is_set_won(7, 6)   # TRUE  — tiebreak
is_set_won(6, 5)   # FALSE — not yet decided
is_set_won(6, 6)   # FALSE — tiebreak still to be played
```

### `make_training_groups()`

Dividing players into balanced groups is a recurring task for coaches.
`make_training_groups()` accepts a vector of player names and an optional
skill level per player. When levels are provided, a snake-draft ensures
every group gets a fair mix of strong and weaker players.

```{r}
players <- c("Jan", "Piet", "Kees", "Greetje", "Joke", "Herma")
levels  <- c(9, 4, 8, 5, 7, 6)

make_training_groups(players, group_size = 3, levels = levels)
```

Without levels, players are shuffled randomly. Use `seed` for reproducibility:

```{r}
make_training_groups(players, group_size = 3, seed = 42)
```

### `generate_round_robin()`

To make sure everyone plays against everyone, `generate_round_robin()` builds
a complete schedule using the circle method. It works with any number of
players; if the count is odd, a bye is added automatically.

```{r}
generate_round_robin(c("Jan", "Piet", "Greetje"), shuffle = FALSE)
```

Use `seed` to get the same randomised draw every time:

```{r}
generate_round_robin(c("Jan", "Piet", "Kees", "Greetje"), seed = 7)
```
